---
title: "Point predictions CRW"
author: "Fletcher Robbins"
date: "2023-11-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(landscapemetrics)
library(tidyverse)
library(sf)
library(raster)
library(terra)
library(gtools) 
library(conflicted)
library(spgwr)
library(spmodel)
library(sp)
library(gstat)
library(spatstat)
library(rje)
library(class)
library(geodata)
```

```{R}
crw <- read_csv("crw.csv") %>%
  mutate_if(is.character, as.factor)
crd <- read_csv("districts.csv")

wi_shp <-
  read_sf("shp/WI_County_Bnds.shp") %>%
  st_transform(crs = 4032) %>%
  rename(County = COUNTY_NAM) %>%
  select(County, geometry)

crw_by_site <- crw %>%
  group_by(District, County, Year, Lon, Lat) %>%
  summarise(meanTotCRW = mean(TotCRW),
            meanNCRW = mean(NorthernCRW),
            meanWCRW = mean(WesternCRW)) %>%
  st_as_sf(coords = c("Lon", "Lat"), crs = 4032)  %>%
  mutate(ID = 1:n())
  #mutate(id = seq_len(n()))
  #mutate(id = row_number())

```{R}
crw_by_site_long <- 
  crw %>%
  group_by(District, County, Year, Lon, Lat) %>%
  summarise(TotalCRW = mean(TotCRW),
            NorthernCRW = mean(NorthernCRW),
            WesternCRW = mean(WesternCRW)) %>%
  ungroup() %>%
  mutate(ID = 1:n()) %>%
  pivot_longer(cols = c(TotalCRW, NorthernCRW, WesternCRW)) %>%
  st_as_sf(coords = c("Lon", "Lat"), crs = 4032)%>%
  group_by(District, County, Lon, Lat) %>%
  summarise(meanTotCRW = mean(TotCRW),
            meanNCRW = mean(NorthernCRW),
            meanWCRW = mean(WesternCRW)) %>%
  st_as_sf(coords = c("Lon", "Lat"), crs = 4032)  %>%
  mutate(ID = 1:n()) 
```

```{R}
crw_by_site_old <-
  crw %>%
  filter(Year <= 2017) %>%
  group_by(District, County, Lon, Lat) %>%
  summarise(meanTotCRW = mean(TotCRW),
            meanNCRW = mean(NorthernCRW),
            meanWCRW = mean(WesternCRW)) %>%
  st_as_sf(coords = c("Lon", "Lat"), crs = 4032)%>%
  mutate(ID = 1:n())

corn_rast <- rast("Crop_Frequency_2008-2022\\crop_frequency_corn_2008-2022.tif")

crw_by_site_old
crw_by_site_new
```
```{R}
g = st_make_grid(wi_shp, cellsize= .075, what='centers')

df1 = data.frame(st_coordinates(g[]))

#crw_df<- data.frame(st_coordinates(df1[]))

#write_csv(crw_df, "crw_df.csv")
#write_csv(df1, "WI_grid.csv")
```

```{R}
WI_grid<- st_make_grid(
  wi_shp,
  #cellsize = .01,
  #offset = st_bbox(x)[c("xmin", "ymin")],
  n = c(25887, 26962 ),
  #crs = if (missing(x)) NA_crs_ else st_crs(x),
  what = "centers"
  #square = TRUE,
  #flat_topped = FALSE
 #, "WI_grid.csv"
)

```
```{r}
df2 = data.frame(st_coordinates(WI_grid[]))
WI_grid
```


```{r}
# lsm function wrapper
lsm_fn <- function(df, rast, dist) {
  # df needs 'ID' column
  # dist in meters, can take multiple values
  require(landscapemetrics)
  require(raster)
  require(dplyr)
  #message("Using landscape: ", rast@file@name)
  for (i in 1:length(dist)) {
    #message("Buffer ", i, " of ", length(dist), ": ", dist[i], "m")
    lsm <-
      sample_lsm(
        landscape = rast,
        y = df,
        #plot_id = df$ID,
        shape = "circle",
        size = dist[i],
        what = "lsm_c_pland",
        progress = TRUE
      ) %>%
      filter(class != 255) %>%
      mutate(area = value * (percentage_inside / 100)) %>%
      mutate(intensity = class * area / 100) %>%
      replace(is.na(.), 0) %>%
      group_by(plot_id) %>%
      summarise(!!paste0("intensity_", dist[i]) := sum(intensity))
    if (i == 1) {lsm_merge <- lsm} else {lsm_merge <- full_join(lsm_merge, lsm)}
  }
  inner_join(lsm_merge, df, by = c("plot_id" = "ID")) %>%
    rename(ID = plot_id) %>%
    st_as_sf(crs = crs(df))
}
```

```{R}
crw_train <-
  crw_by_site_old %>%
  st_transform(crs(corn_rast))

crw_test <-
  crw_by_site_new %>%
  st_transform(crs(corn_rast))


crw_by_site <- 
  crw_by_site %>%
  st_transform(crs(corn_rast))

crw_lsm1 <- crw_train %>% lsm_fn(corn_rast, c(5000))
crw_train_df <- crw_lsm1 %>%
  st_transform(crs = 4032) %>%
  mutate(lon = st_coordinates(.)[, "X"],
         lat = st_coordinates(.)[, "Y"]) %>%
  st_set_geometry(NULL)


crw_lsm2 <- crw_test %>% lsm_fn(corn_rast, c(5000))
crw_test_df <- crw_lsm2 %>%
  st_transform(crs = 4032) %>%
  mutate(lon = st_coordinates(.)[, "X"],
         lat = st_coordinates(.)[, "Y"]) %>%
  st_set_geometry(NULL)

crw_lsm3 <- crw_by_site %>% lsm_fn(corn_rast, c(5000))
crw_df <- crw_lsm3 %>%
  st_transform(crs = 4032) %>%
  mutate(lon = st_coordinates(.)[, "X"],
         lat = st_coordinates(.)[, "Y"]) %>%
  st_set_geometry(NULL)
```

```{R}
crw_train_df
crw_test_df 
crw_df

crw_train_df1 <- crw_train_df
crw_test_df1 <- crw_test_df
crw_df1 <- crw_df

model1 <- lm(lon~ intensity_5000+ meanTotCRW, data=crw_train_df)
model2 <- lm(lat~ intensity_5000+ meanTotCRW, data=crw_train_df)

lat_pred<- predict(model1, newdata = crw_test_df)
lon_pred<- predict(model2, newdata = crw_test_df)

df<- data.frame(lon= predict(model1, newdata = crw_test_df), lat= predict(model2, newdata = crw_test_df))
qplot(lon,lat,data=df)  +geom_point(data=crw_test_df,colour='red') 

#coordinates(crw_df) = ~lon+lat

spbb <- st_as_sf(crw_df, crs = 4032)          
dist_matrix   <- st_distance(spbb, spbb)
diag(dist_matrix) <- NA
spbb$avg  <- rowMeans(dist_matrix)


```

```{R}
#coordinates(crw_train_df) = ~lon+lat
#coordinates(crw_test_df) = ~lon+lat

#crw_train_df <- st_as_sf(crw_train_df, crs = 4032)          
km<- kmeans(crw_df1[7:8], 400, 5)
crw_df1$cluster <- km$cluster

df<- crw_df1 %>%
  group_by(cluster) %>%
  summarise_at(vars(meanTotCRW), list(name=sd))
ggplot(df, aes(x=name)) + geom_histogram()
```

```{R}
crw_df1 <- st_as_sf(crw_df1, crs = 4032)

crw.vgm<- variogram(log(meanTotCRW)~1, crw_df1, cutoff= 150)
#crw.vgm<- variogram(intensity_5000~1, crw_df1)
crw.fit <- fit.variogram(crw.vgm, model=vgm("Sph"))
plot(crw.vgm,crw.fit)

g = st_make_grid(crw_df1, cellsize= .075, what='centers')

plot(g)
plot(st_geometry(crw_df1) , add = TRUE)
df1 = data.frame(st_coordinates(g[]))

#crw.kriged <- krige(meanTotCRW~1, crw_df1, g, model=crw.fit)

#crw.kriged <- krige(meanTotCRW~1, crw_df1, g, model=crw.fit)
crw.kriged %>% as.data.frame %>%
  ggplot(aes(x=x, y=y)) + geom_tile(aes(fill=var1.pred)) + coord_equal() +
  scale_fill_gradient(low = "yellow", high="red") +
  #scale_x_continuous(labels=comma) + scale_y_continuous(labels=comma) +
  theme_bw()
```
```{r}
Lawton <-  read_csv('C:\\Users\\frobb\\Documents\\Data\\Evolutionary Rates\\Lawton_etal_data.csv') %>%
  mutate_if(is.character, as.factor)
Lawton
```
```{R}
wi_shp <-
  read_sf("shp/WI_County_Bnds.shp") %>%
  st_transform(crs = 4032) %>%
  rename(County = COUNTY_NAM) %>%
  select(County, geometry)

crw_by_site <- Lawton %>%
  group_by(District, County, Year, Lon, Lat) %>%
  summarise(meanTotCRW = mean(TotCRW),
            meanNCRW = mean(NorthernCRW),
            meanWCRW = mean(WesternCRW)) %>%
  st_as_sf(coords = c("Lon", "Lat"), crs = 4032)  %>%
  mutate(ID = 1:n())
  #mutate(id = seq_len(n()))
  #mutate(id = row_number())


corn_rast <- rast("Crop_Frequency_2008-2022\\crop_frequency_corn_2008-2022.tif")
```



```{R}
#cropland(source= 'WorldCover' , path= "C:\\Users\\frobb\\Downloads", year=2003)
footprint(year= 2009, path="C:\\Users\\frobb\\Downloads")
```

